---
title: "betaMC"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![CRAN Status](https://www.r-pkg.org/badges/version/betaMC)](https://cran.r-project.org/package=betaMC)
[![R-Universe Status](https://jeksterslab.r-universe.dev/badges/betaMC)](https://jeksterslab.r-universe.dev)
[![R-CMD-check](https://github.com/jeksterslab/betaMC/workflows/R-CMD-check/badge.svg)](https://github.com/jeksterslab/betaMC/actions)
[![test-coverage](https://github.com/jeksterslab/betaMC/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/jeksterslab/betaMC/actions/workflows/test-coverage.yaml)
[![lint](https://github.com/jeksterslab/betaMC/actions/workflows/lint.yaml/badge.svg)](https://github.com/jeksterslab/betaMC/actions/workflows/lint.yaml)
[![codecov](https://codecov.io/gh/jeksterslab/betaMC/branch/main/graph/badge.svg?token=KVLUET3DJ6)](https://codecov.io/gh/jeksterslab/betaMC)
<!-- badges: end -->

## Description

Generates Monte Carlo confidence intervals
for standardized regression coefficients (beta) and other effect sizes,
including multiple correlation, semipartial correlations,
improvement in R-squared, squared partial correlations,
and differences in standardized regression coefficients,
for models fitted by `lm()`.
`betaMC` combines ideas from Monte Carlo confidence intervals for the indirect effect
(Preacher and Selig, 2012: http://doi.org/10.1080/19312458.2012.679848)
and the sampling covariance matrix of regression coefficients
(Dudgeon, 2017: http://doi.org/10.1007/s11336-017-9563-z)
to generate confidence intervals effect sizes in regression.

## Installation

You can install the CRAN release of `betaMC` with:

```r
install.packages("betaMC")
```

You can install the development version of `betaMC` from
[GitHub](https://github.com/jeksterslab/betaMC) with:

```r
if (!require("remotes")) install.packages("remotes")
remotes::install_github("jeksterslab/betaMC")
```

## Example

In this example, a multiple regression model is fitted
using program quality ratings (`QUALITY`) as the regressand/outcome variable
and number of published articles attributed to the program faculty members (`NARTIC`),
percent of faculty members holding research grants (`PCTGRT`), and
percentage of program graduates who received support (`PCTSUPP`) as regressor/predictor variables
using a data set from 1982 ratings of 46 doctoral programs in psychology in the USA (National Research Council, 1982).
Confidence intervals for the standardized regression coefficients are generated
using the `BetaMC()` function from the `betaMC` package.

```{r}
#| message = FALSE
library(betaMC)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaMC"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
#| eval = FALSE
df <- betaMC::nas1982
```

### Regression

Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

### Monte Carlo Sampling Distribution of Parameters

#### Normal-Theory Approach

```{r}
mvn <- MC(object, type = "mvn")
```

#### Asymptotic distribution-free Approach

```{r}
adf <- MC(object, type = "adf")
```

#### Heteroskedasticity Consistent Approach (HC3)

```{r}
hc3 <- MC(object, type = "hc3")
```

### Standardized Regression Slopes

#### Normal-Theory Approach

```{r}
BetaMC(mvn, alpha = 0.05)
```

#### Asymptotic distribution-free Approach

```{r}
BetaMC(adf, alpha = 0.05)
```

#### Heteroskedasticity Consistent Approach (HC3)

```{r}
BetaMC(hc3, alpha = 0.05)
```

### Other Effect Sizes

The `betaMC` package also has functions to generate Monte Carlo confidence intervals
for other effect sizes such as
`RSqMC()` for multiple correlation coefficients (R-squared and adjusted R-squared),
`DeltaRSqMC()` for improvement in R-squared,
`SCorMC()` for semipartial correlation coefficients,
`PCorMC()` for squared partial correlation coefficients,
and
`DiffBetaMC()` for differences of standardized regression coefficients.

#### Multiple Correlation Coefficients (R-squared and adjusted R-squared)

```{r}
RSqMC(hc3, alpha = 0.05)
```

#### Improvement in R-squared

```{r}
DeltaRSqMC(hc3, alpha = 0.05)
```

#### Semipartial Correlation Coefficients

```{r}
SCorMC(hc3, alpha = 0.05)
```

#### Squared Partial Correlation Coefficients

```{r}
PCorMC(hc3, alpha = 0.05)
```

#### Differences of Standardized Regression Coefficients

```{r}
DiffBetaMC(hc3, alpha = 0.05)
```

### References

Dudgeon, P. (2017).
Some improvements in confidence intervals for standardized regression coefficients. 
*Psychometrika*, *82*(4), 928–951.
https://doi.org/10.1007/s11336-017-9563-z

National Research Council. (1982).
*An assessment of research-doctorate programs in the United States: Social and behavioral sciences*.
https://doi.org/10.17226/9781.
Reproduced with permission from the National Academy of Sciences,
Courtesy of the National Academies Press, Washington, D.C.

Pesigan, I. J. A. (2022).
Confidence intervals for standardized coefficients:
Applied to regression coefficients in primary studies and indirect effects in meta-analytic structural equation modeling [Unpublished doctoral dissertation].
University of Macau. 

Preacher, K. J., & Selig, J. P. (2012).
Advantages of Monte Carlo confidence intervals for indirect effects.
*Communication Methods and Measures*, *6*(2), 77-98.
https://doi.org/10.1080/19312458.2012.679848

## Documentation

See
[GitHub Pages](https://jeksterslab.github.io/betaMC/index.html)
for package documentation.
